```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Reproducible Research: Peer Assessment 1

###Loading and preprocessing the data

####1. Load the data (i.e. read.csv())

```{r message = FALSE, warning = FALSE}
library(ggplot2)
library(scales)
library(Hmisc)
```

```{r}
if(!file.exists('activity.csv')){
        unzip('activity.zip')
}
activityData <- read.csv('activity.csv')
```

###What is mean total number of steps taken per day?

####1. Calculate the total number of steps taken per day

```{r}
stepsByDay <- tapply(activityData$steps, activityData$date, sum, na.rm = TRUE)
```

####2. Make a histogram of the total number of steps taken each day

```{r}
qplot(stepsByDay, xlab ='Total Steps Per Day', ylab='Frequency', binwidth=500)
```


####3. Calculate and report the mean and median of the total number of steps taken per day
```{r}
meanStepsByDay <- mean(stepsByDay)
medianStepsByDay <- median(stepsByDay)
```

######Mean: 
```{r}
meanStepsByDay
```

######Median:
```{r}
medianStepsByDay
```

###What is the average daily activity pattern?

```{r}
averageStepsPerInterval <- aggregate(x=list(meanSteps=activityData$steps), by=list(interval=activityData$interval), FUN=mean, na.rm=TRUE)
```


####1. Make a time series plot (i.e. type = "l") of the 5-minute interval (x-axis) and the average number of steps taken, averaged across all days (y-axis)

```{r}
ggplot(data=averageStepsPerInterval, aes(x=interval, y=meanSteps))+
        geom_line()+
        xlab("5-minute interval")+
        ylab("average number of steps taken")
```


####2. Which 5-minute interval, on average across all the days in the dataset, contains the maximum number of steps?

```{r}

```

